\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
slight additions to implementation section

In addition to this optimization, we also use a native C implementation of the
Levenshtein function.  We do not compare this to any Ruby implementation, but
we suspect it has some nontrivial impact on runtime due to the volume of calls
to the function.

>>>>

In addition to this optimization, we also use a native C implementation of the
Levenshtein function. In early versions of our program,
since every pair of variable expansions must be compared,
our Ruby implementation of a longest-common-subsequence algorithm was by far the
largest bottleneck. Replacing it with a native C implementation of levenshtein
distance improved performance dramatically. Though both implementations have the
same $O(n^2)$ asymptotic runtime, the constants in the native implementation
are so small that calls to levenshtein take nearly negligible time on the data
sizes we were able to test.
